Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2021-12-27 paper.tex
Remove space
Add comment on recommending use of noise in instability study
Add more discussion on ansiotropy in discussion

@@

As the current distribution, which develops as the flux tube is twisted, is
similar to that found in the initial flux tube configuration
of~\cite{quinnEffectAnisotropicViscosity2020},the question arises why the
fluting instability is not observed in the latter. Although the current
distribution (and thus heating and pressure distributions) in the tubes
of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute
instability, the tube is initially perturbed with a motion close to an unstable
eigenmode of the kink instability, resulting in the instability growing from
$t=0$. In contrast, in the tubes studied here, such a perturbation must build
from numerical noise, allowing a secondary, fluting perturbation to also build
and become significant enough to observe.

@@

The form of viscosity has been found to significantly affect the growth of the
flute instability. Importantly, isotropic viscosity is found to damp the growth
of the flute instability to the degree that it is unable to grow appreciably
before the onset of the faster growing nonlinear kink instability. Overall, the
anisotropic model permits greater release of kinetic energy. Similar to~\citet{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating is found
to be lower than anisotropic (switching) viscous heating, by approximately two
orders of magnitude.

>>>>

\rev{We have found evidence of the flute instability using both models of
viscosity, however isotropic viscosity damps the initial growth such that it
does not develop beyond its linear phase before the faster growing kink
instability disrupts the flux tube and halts the development of the flute. Due
to the enhanced growth of the flute instability in the anisotropic case, the
tube becomes more readily mixed and the growth rate of the kink instability is
smaller. Beyond the effect on the growth of the two observed instabilities, the
two viscosity models greatly affect both the viscous heating and Ohmic heating
rates. Anisotropic viscosity is naturally less dissipative than isotropic
viscosity and results in viscous heating approximately two orders of magnitude
less than that associated with isotropic viscosity. This is somewhat offset by
the anisotropic viscosity model permitting greater kinetic energy release and
enhanced mixing, which in turn enhances Ohmic dissipation of heat through the
generation of small, strong current sheets. The overall effect is that more
heat is released when the viscosity is anisotropic. This is similarly observed
in previous work~\citep{quinnEffectAnisotropicViscosity2020}.}

@@

As the current distribution, which develops as the flux tube is twisted, is
similar to that found in the initial flux tube configuration
of~\cite{quinnEffectAnisotropicViscosity2020},the question arises why the
fluting instability is not observed in the latter. Although the current
distribution (and thus heating and pressure distributions) in the tubes
of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute
instability, the tube is initially perturbed with a motion close to an unstable
eigenmode of the kink instability, resulting in the instability growing from
$t=0$. In contrast, in the tubes studied here, such a perturbation must build
from numerical noise, allowing a secondary, fluting perturbation to also build
and become significant enough to observe. \rev{As an explorative alternative to
prescriptive perturbations, we recommend the use of numerical noise in the
study of coronal instabilities.}

@@
